A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-02 paper/ms.tex
update ms

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr
\citep{meibom_kepler_2011}.  Though isochronal, gyrochronal, and lithium-based
analyses suggest that younger Kepler planets do exist
\citep{berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the Gaia
data have greatly expanded our knowledge of cluster memberships
\citep[{\it
e.g.},][]{cantatgaudin_gaia_2018,zari_3d_2018,kounkel_untangling_2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

Matching our young star list against stars observed by Kepler revealed that
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
Kepler observed a portion of the \cn\ (Stephenson-1;
Theia~73).
More specifically, a clustering analysis of the Gaia
data by \citet{kounkel_untangling_2019}
reported that Kepler~1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
\cn\ member.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and 
in 
Section~\ref{sec:stars} show
that \sn\ is both a binary and also a member of the cluster.
Focusing on the planet (Section~\ref{sec:planet}), we confirm that despite the
presence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
may also be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Galactic positions and tangential velocities of stars in the
			$\delta$\,Lyr cluster.} Points are reported cluster members from
		\citet{kounkel_untangling_2019}.  
		The tangential velocities relative to
		\sn\ (lower-right) are computed assuming that every star has the same
		three-dimensional spatial velocity as \sn.
		Our analysis uses stars (black points)
		in the spatial and kinematic vicinity of Kepler\,1627 (yellow
		star).  The question of whether the other candidate cluster members
		(gray points) are part of the cluster is outside our scope.  The
		location of the Sun is ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\citet{kounkel_untangling_2019} applied an unsupervised clustering
algorithm to Gaia DR2 on-sky positions, proper motions, and
parallaxes for stars within the nearest kiloparsec.  For the \cn\
(Theia 73), they reported \noriginal\ candidate members.  We
matched these stars against the latest Gaia EDR3 observations using
the \texttt{dr2\_neighbourhood} table from the ESA archive\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.},
and took the closest proper motion and epoch-corrected angular
distance as the presumed match
\citep{gaia_collaboration_2021_edr3}.  In Figure~\ref{fig:XYZvtang},
have shown galactic positions only for the stars with
parallax signal-to-noise exceeding 20.  The reported cluster members
(gray and black points) extend over a much larger volume than the
cluster previously identified by \citet{stephenson_possible_1959} and
later corroborated by \citet{eggen_photometric_1968}.  While the
non-uniform ``clumps'' of stars might comprise a {\it bona fide}
cluster of identically-aged stars, they could also be heavily
contaminated by field stars.  We therefore considered stars only in
the immediate kinematic and spatial vicinity of \sn\ as candidate
cluster members.  We performed the selection cuts manually, by
drawing lassos with the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  The overlap between the Kepler
field and the resulting candidate cluster members is shown in
Figure~\ref{fig:skychart}.  While this method will
include some field interlopers in the ``cluster star'' sample, and
vice-versa, it should suffice for our aim of verifying the existence
of the cluster in the vicinity of \sn.

@@

We measured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602, the Pleiades, and the
field.  
The stars from the Pleiades and IC\,2602 were adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}, 2021/09/25},
and applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} assuming that $A_0 = 3.1
E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.  To turn this heuristic interpolation into an age
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{damiani_stellar_2019} and
\cite{CantatGaudin2018a} respectively.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the
CAMD.  We then passed a moving box average and standard deviation
across the CAMD in 0.10\,mag bins, fitted a univariate spline to the
binned values, and assembled a piecewise grid of hybrid isochrones
spanning the ages between UCL to the Pleiades using Equations~6 and~7
from \citet{gagne_mutau_2020}.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{kounkel_untangling_2019}, \nwithtess\ stars were amenable to
rotation period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS
full frame image data.\footnote{Kepler rotation periods were derived
by \citet{mcquillan_rotation_2014} for 28 stars; for these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 and
2.5 TESS magnitudes of the target star.

@@

% \section{Kinematic Selection of $\delta$\,Lyr Cluster Members}
% \label{app:kinematicselection}
% 
% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=1\textwidth]{f6.pdf}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{
%     {\bf Galactic position and tangential velocities of the
%     $\delta$\,Lyr cluster.}
%     Points are candidate cluster members with $\varpi/\sigma_\varpi >
%     20$, reported to be in the group by
%     \citet{kounkel_untangling_2019}.  We focus on stars (black points)
%     in the spatial and kinematic vicinity of Kepler\,1627 (yellow
%     star).  The other candidate cluster members (gray points) may or
%     may not share the ages of the selected kinematic group.  The
%     location of the Sun is ($\odot$) is shown.
% 		\label{fig:XYZvtang}
% 	}
% \end{figure*}
% 
% Figure~\ref{fig:XYZvtang} shows stars reported by
% \citet{kounkel_untangling_2019} to be in the group ``Theia 73'', which
% was cross-matched by Kounkel \& Covey as being ``Stephenson 1''.
% \citet{kounkel_untangling_2019} reported \noriginal\ stars to be
% present in this cluster.  For our Figure, galactic positions were
% calculated and plotted only for stars with parallax signal-to-noise
% exceeding 20.  The location of the Sun is shown on the plots.  The
% smattering of reported cluster members (gray and black points) has a
% significantly different structure than the cluster initially
% identified by \citet{stephenson_possible_1959} and corroborated by
% \citet{eggen_photometric_1968}.  While the non-uniform ``clumps''
% might be part of a real structure, they could also be an artifact of
% the data processing steps performed by
% \citet{kounkel_untangling_2019}.  We therefore opted to only consider
% stars in the immediate kinematic and spatial vicinity of \sn.  The
% tangential velocities relative to \sn\ are shown in the bottom right
% panel.  These are computed by assuming that every star has the same
% three-dimensional spatial velocity as \sn, where we assume a systemic
% radial velocity of $-16.7 \pm 0.2$\,\kms\ based on the HIRES
% spectra.  The
% relevant projection effects are then taken into account, as discussed
% by {\it e.g.}, \citet{Meingast2021} and \citet{bouma_2021_ngc2516}.
% We performed the actual selection by then manually drawing lassos with
% the interactive \texttt{glue} visualization tool
% \citep{beaumont_2014_13866} in the four projections shown in
% Figure~\ref{fig:XYZvtang}.  While other cluster members likely exist
% outside of our selection region (and our selection also includes some
% field star interlopers), our aim is to verify the existence of the
% cluster in the vicinity of Kepler\,1627, and to measure its age.  The
% procedure we have adopted enables both tasks.

@@

\subsection{Is the Transit Asymmetry Robust?}

@@

\subsection{Possible Explanations}

@@

The expectation however is for the starspot-induced signals to be smooth,
at worst with contributions at $0.5\,P_{\rm rot}$ or $0.25\,P_{\rm
rot}$ \citep{klein_simulated_2020}.  We therefore fitted the RVs using
the \citet{hirano_analytic_2010,hirano_2011} models for the
Rossiter-McLaughlin (RM) effect, and allowed for an optional linear
and quadratic trend in time to fit the $\approx$250\ms\ spot-induced trend.  We
followed the methodology developed by \citet{stefansson_2020}.  We
allowed the sky-projected obliquity, the projected stellar equatorial
velocity, and the Gaussian dispersion of the spectral lines to vary,
and fixed the limb-darkening using the $V$-band tabulation from
\citet{claret_gravity_2011}.  We assumed a Gaussian prior on $v\sin i$ and
$a/R_\star$ from Table~\ref{tab:starparams}, and also allowed for a
white-noise jitter term to be added in quadrature to the measurement
uncertainties.
We used the 15\,minute exposure time when numerically evaluating the
model.

@@

The amplitude of both the spot-induced trend and the jitter are
somewhat larger than recent comparable measurements in systems such as
AU~Mic \citep{palle_transmission_2020}, DS~Tuc
\citep{montet_young_2020,zhou_well_2020} and TOI~942
\citep{wirth_2021_toi942}.  One possible explanation for the jitter is
that it is astrophysical in origin, and that it is caused by some
novel process operating on the surface of Kepler 1627A.  Another
possibility is that our RV analysis underestimates our measurement
uncertainties; in order to achieve the requisite time-sampling the S/N
per resolution element in our spectra was 70 to 80, which is lower
than desired for deriving high-precision velocities.  In addition, the
rapid rotation of the star could affect accuracy of the uncertainties
from the velocity extraction.  Observations at higher S/N are
necessary to distinguish these two possibilities, and remain
worthwhile in order to clarify the orbital geometry of \pn.  Useful
next steps would include transit observations with a stabilized
optical spectrograph, or potentially also observations in the
near-infrared \citep[{\it e.g.},][]{feinstein_halpha_2021}.

>>>>

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr
\citep{meibom_kepler_2011}.  Though isochronal, gyrochronal, and lithium-based
analyses suggest that younger Kepler planets do exist
\citep{berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the Gaia
data have greatly expanded our knowledge of cluster memberships
\citep[{\it
e.g.},][]{CantatGaudin2018a,Zari2018,KounkelCovey2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

Matching our young star list against stars observed by Kepler revealed that
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
Kepler observed a portion of the \cn\ (Stephenson-1;
Theia~73).
More specifically, a clustering analysis of the Gaia
data by \citet{KounkelCovey2019}
reported that Kepler~1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
\cn\ member.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and 
in 
Section~\ref{sec:stars} show
that \sn\ is both a binary and also a member of the cluster.
Focusing on the planet (Section~\ref{sec:planet}), we confirm that despite the
presence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
may also be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Galactic positions and tangential velocities of stars in the
			$\delta$\,Lyr cluster.} Points are reported cluster members from
		\citet{KounkelCovey2019}.  
		The tangential velocities relative to
		\sn\ (lower-right) are computed assuming that every star has the same
		three-dimensional spatial velocity as \sn.
		Our analysis uses stars (black points)
		in the spatial and kinematic vicinity of Kepler\,1627 (yellow
		star).  The question of whether the other candidate cluster members
		(gray points) are part of the cluster is outside our scope.  The
		location of the Sun is ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\citet{KounkelCovey2019} applied an unsupervised clustering
algorithm to Gaia DR2 on-sky positions, proper motions, and
parallaxes for stars within the nearest kiloparsec.  For the \cn\
(Theia 73), they reported \noriginal\ candidate members.  We
matched these stars against the latest Gaia EDR3 observations using
the \texttt{dr2\_neighbourhood} table from the ESA archive\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.},
and took the closest proper motion and epoch-corrected angular
distance as the presumed match
\citep{gaia_collaboration_2021_edr3}.  In Figure~\ref{fig:XYZvtang},
have shown galactic positions only for the stars with
parallax signal-to-noise exceeding 20.  The reported cluster members
(gray and black points) extend over a much larger volume than the
cluster previously identified by \citet{stephenson_possible_1959} and
later corroborated by \citet{eggen_photometric_1968}.  While the
non-uniform ``clumps'' of stars might comprise a {\it bona fide}
cluster of identically-aged stars, they could also be heavily
contaminated by field stars.  We therefore considered stars only in
the immediate kinematic and spatial vicinity of \sn\ as candidate
cluster members.  We performed the selection cuts manually, by
drawing lassos with the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  The overlap between the Kepler
field and the resulting candidate cluster members is shown in
Figure~\ref{fig:skychart}.  While this method will
include some field interlopers in the ``cluster star'' sample, and
vice-versa, it should suffice for our aim of verifying the existence
of the cluster in the vicinity of \sn.

@@

We measured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602, the Pleiades, and the
field.  
The stars from the Pleiades and IC\,2602 were adopted from
\citet{CantatGaudin2018a}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}, 2021/09/25},
and applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} assuming that $A_0 = 3.1
E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.  To turn this heuristic interpolation into an age
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the
CAMD.  We then passed a moving box average and standard deviation
across the CAMD in 0.10\,mag bins, fitted a univariate spline to the
binned values, and assembled a piecewise grid of hybrid isochrones
spanning the ages between UCL to the Pleiades using Equations~6 and~7
from \citet{gagne_mutau_2020}.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{KounkelCovey2019}, \nwithtess\ stars were amenable to
rotation period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS
full frame image data.\footnote{Kepler rotation periods were derived
by \citet{mcquillan_rotation_2014} for 28 stars; for these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 and
2.5 TESS magnitudes of the target star.

@@

% \section{Kinematic Selection of $\delta$\,Lyr Cluster Members}
% \label{app:kinematicselection}
% 
% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=1\textwidth]{f6.pdf}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{
%     {\bf Galactic position and tangential velocities of the
%     $\delta$\,Lyr cluster.}
%     Points are candidate cluster members with $\varpi/\sigma_\varpi >
%     20$, reported to be in the group by
%     \citet{KounkelCovey2019}.  We focus on stars (black points)
%     in the spatial and kinematic vicinity of Kepler\,1627 (yellow
%     star).  The other candidate cluster members (gray points) may or
%     may not share the ages of the selected kinematic group.  The
%     location of the Sun is ($\odot$) is shown.
% 		\label{fig:XYZvtang}
% 	}
% \end{figure*}
% 
% Figure~\ref{fig:XYZvtang} shows stars reported by
% \citet{KounkelCovey2019} to be in the group ``Theia 73'', which
% was cross-matched by Kounkel \& Covey as being ``Stephenson 1''.
% \citet{KounkelCovey2019} reported \noriginal\ stars to be
% present in this cluster.  For our Figure, galactic positions were
% calculated and plotted only for stars with parallax signal-to-noise
% exceeding 20.  The location of the Sun is shown on the plots.  The
% smattering of reported cluster members (gray and black points) has a
% significantly different structure than the cluster initially
% identified by \citet{stephenson_possible_1959} and corroborated by
% \citet{eggen_photometric_1968}.  While the non-uniform ``clumps''
% might be part of a real structure, they could also be an artifact of
% the data processing steps performed by
% \citet{KounkelCovey2019}.  We therefore opted to only consider
% stars in the immediate kinematic and spatial vicinity of \sn.  The
% tangential velocities relative to \sn\ are shown in the bottom right
% panel.  These are computed by assuming that every star has the same
% three-dimensional spatial velocity as \sn, where we assume a systemic
% radial velocity of $-16.7 \pm 0.2$\,\kms\ based on the HIRES
% spectra.  The
% relevant projection effects are then taken into account, as discussed
% by {\it e.g.}, \citet{Meingast2021} and \citet{bouma_2021_ngc2516}.
% We performed the actual selection by then manually drawing lassos with
% the interactive \texttt{glue} visualization tool
% \citep{beaumont_2014_13866} in the four projections shown in
% Figure~\ref{fig:XYZvtang}.  While other cluster members likely exist
% outside of our selection region (and our selection also includes some
% field star interlopers), our aim is to verify the existence of the
% cluster in the vicinity of Kepler\,1627, and to measure its age.  The
% procedure we have adopted enables both tasks.

@@

\subsection{How Robust is the Asymmetric Transit?}

@@

\subsection{Interpretation}

@@

The expectation however is for the starspot-induced signals to be smooth,
at worst with contributions at $0.5\,P_{\rm rot}$ or $0.25\,P_{\rm
rot}$ \citep{klein_simulated_2020}.  We therefore fitted the RVs using
the \citet{hirano_analytic_2010,hirano_2011} models for the
Rossiter-McLaughlin (RM) effect, and allowed for an optional linear
and quadratic trend in time to fit the $\approx$250\ms\ spot-induced trend.  We
followed the methodology developed by \citet{stefansson_2020}.  We
allowed the sky-projected obliquity, the projected stellar equatorial
velocity, and the Gaussian dispersion of the spectral lines to vary,
and fixed the limb-darkening using the $V$-band tabulation from
\citet{claret_gravity_2011}.  We assumed a Gaussian prior on $v\sin i$ and
$a/R_\star$ from Table~\ref{tab:starparams}, and also allowed for a
white-noise jitter term to be added in quadrature to the measurement
uncertainties.
We used a 15\,minute exposure time to numerically evaluate the
model.

@@

The amplitude of both the spot-induced trend and the jitter are
somewhat larger than recent comparable measurements in systems such as
AU~Mic \citep{palle_transmission_2020}, DS~Tuc
\citep{montet_young_2020,zhou_well_2020} and TOI~942
\citep{wirth_2021_toi942}.  One possible explanation for the jitter is
that it is astrophysical in origin, and that it is caused by some
novel process operating on the surface of Kepler 1627A.  Another
possibility is that our RV analysis underestimates our measurement
uncertainties; in order to achieve the requisite time-sampling the S/N
per resolution element in our spectra was 70 to 80, which is lower
than desired for deriving high-precision velocities.  In addition, the
rapid rotation of the star could affect accuracy of the uncertainties
from the velocity extraction.  Observations at higher S/N are
necessary to distinguish these two possibilities, and remain
worthwhile in order to clarify the orbital geometry of \pn.  Useful
next steps would include transit observations with a stabilized
spectrograph in the optical \citep[{\it
e.g.},][]{gibson_2016_kpf,seifahrt_maroon-x_2018}, or in the near-infrared
\citep[{\it e.g.},][]{feinstein_halpha_2021}.
